The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-08-13 paper/ms.tex
6 cosmic variance graphs

@@

@@

>>>>

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD2_CosmicVar1_wo_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Bouwens data in the no-dust
 attenuation model.}
\label{fig:OD2_CosmicVar1_wo_dust}
\end{figure}

@@

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD3_CosmicVar1_wo_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with McLure data in the no-dust
 attenuation model.}
\label{fig:OD3_CosmicVar1_wo_dust}
\end{figure}

@@

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD4_CosmicVar1_wo_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Finkelstein data in the no-dust
 attenuation model.}
\label{fig:OD4_CosmicVar1_wo_dust}
\end{figure}
